\centering \textbf{Abstract}

\iffalse
    In camera pre-calibration, images of a calibration object are commonly 
    used to determine the internal geometry of a camera.
    The calibration imaging is often optimized to have the calibration object 
    cover as large image area as possible.
    This is likely to yield a larger concentration
    of measured image points near the center of the image sensor.
    In this report, the hypothesis is investigated that this 
    non-uniform image point distribution results in a sub-optimal calibration.
    An area-based re-weighting scheme is suggested to improve the calibration.
    Additionally, the effect of a choice between a 2D and a 3D calibration
    object is investigated.
    
    A simulation study was performed where both a standard and area-weighted
    pre-calibration scheme was used in a parallel and a convergent scene.
    The estimated uncertainty and true errors were computed
    and compared to the first order predictions and results of perfect calibrations.
    The area-based calibration showed no reduction in estimation errors.
    Furthermore, the 3D calibration object did not give a noticeable improvement.
    However, for the standard and area-based calibrations, the true errors
    surpassed the estimated uncertainties by up to
    26 and 58 percent, respectively.
\fi

	In payment channel network, such as the lightning network, the routing
	nodes receives a fee as compensation for displaced liquidity and operational
	costs. Currently this fee is mostly manually set procuring an unoptimized profit to
	the node operator. TODO: TYPES OF POLICIES HERE, NOT ONLT PRICE BIT PREFERENTIAL ATTACHMENT, RECEIVED CHANNELS
	AND OPTIMAL STRATEGY AS PRODUCT OF OTHERS STRATEGIES; HENCE GAME THEORY. 
	
	A simulation study was performed where many policies was pitted against 
	each other to find emergent equilibria under competitive market pressure. Were such
	equilibrium may lie have further consequences for the network in form
	of total throughput, routing cost and robustness.
		 
	
	